Inpainting with controlled frequency suppression in the Fourier domain

### 2011-06-23 project/Paper/paper.tex
Paper: Removed and scaled images, minor corrections.

\subsubsection{Gradient descent}
\label{gradient_descent}
We optimize all parameters at once using a gradient descent method. Since our cost function is based on measurements, we cannot derive it with respect to individual parameters and have to determine the gradient with finite differences. Besides weighting the parameters with respect to their improvements (which gives us the slope), we also defined a momentum term of 0.8 that should help us to overcome local minima and improve convergence speed. Figure \ref{gradient_descent_cost} shows the development of the cost for 100 optimisation steps.

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{../plots/cost_plot.pdf}
\caption{Due to the momentum term, the cost function does not strictly decrease when optimising.}
\label{gradient_descent_cost}
\end{figure}

@@

\begin{figure*}
  \centering
  \subfloat{\includegraphics[width=0.22\textwidth]{../daisiesFromBing512x512}}~
  \subfloat{\includegraphics[width=0.22\textwidth]{../hardedges_512x512}}~
  \subfloat{\includegraphics[width=0.22\textwidth]{../penguinsFromBing512x512}}~
  \subfloat{\includegraphics[width=0.22\textwidth]{../velos512x512}}~
  \caption{The four additional images used during the optimisation.}
  \label{new_images}
\end{figure*}

@@

\begin{figure}
  \centering
  \subfloat{\label{fig:gull}\includegraphics[width=0.25\textwidth]{../plots/td_middle_plot.pdf}}                
  \subfloat{\label{fig:tiger}\includegraphics[width=0.25\textwidth]{../plots/validation_plot.pdf}}
  \caption{Two parameters that seem to converge quite well during the optimisation.}
  \label{gradient_descent_parameters}
\end{figure}

\section{Results}
We compared our algorithm with the following three baseline algorithms (see figure \ref{baseline_algorithms}):
\begin{enumerate}
\item Vertical and horizontal linear interpolation,
\item Gaussian interpolation as described in section \ref{gaussian_interpolation} and
\item Matching pursuit~\cite{matchingpursuit93} with an overcomplete dictionary of discrete cosines. TODO this reference is wrong!
\end{enumerate}

@@

Since our algorithm did not perform equally well for all sample images, we print those for which it worked best and worst as figures \ref{best_image} and \ref{worst_image}.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Best image with error ? and standard deviation ?.}
\label{best_image}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Worst image with error ? and standard deviation ?.}
\label{worst_image}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Original image with mask (left) and its reconstruciton (right).}
\label{edge_reconstruction}
\end{figure}

>>>>

\subsubsection{Gradient descent}
\label{gradient_descent}
We optimize all parameters at once using a gradient descent method. Since our cost function is based on measurements, we cannot derive it with respect to individual parameters and have to determine the gradient with finite differences. Besides weighting the parameters with respect to their improvements (which gives us the slope), we also defined a momentum term of 0.8 that should help us to overcome local minima and improve convergence speed. Figure \ref{gradient_descent_cost} shows the development of the cost for 100 optimization steps.

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{../plots/cost_plot.pdf}
\caption{Due to the momentum term, the cost function does not strictly decrease when optimizing.}
\label{gradient_descent_cost}
\end{figure}

@@

\begin{figure*}
  \centering
  \subfloat{\includegraphics[width=0.24\textwidth]{../daisiesFromBing512x512}}~
  \subfloat{\includegraphics[width=0.24\textwidth]{../penguinsFromBing512x512}}~
  \subfloat{\includegraphics[width=0.24\textwidth]{../velos512x512}}~
  \subfloat{\includegraphics[width=0.24\textwidth]{../hardedges_512x512}}~
  \caption{The four additional images used during optimization.}
  \label{new_images}
\end{figure*}

@@

\begin{figure}
  \centering
  \subfloat{\label{fig:gull}\includegraphics[width=0.25\textwidth]{../plots/td_middle_plot.pdf}}                
  \subfloat{\label{fig:tiger}\includegraphics[width=0.25\textwidth]{../plots/validation_plot.pdf}}
  \caption{Two parameters that seem to converge quite well during the optimization.}
  \label{gradient_descent_parameters}
\end{figure}

\section{Results}
We compared our algorithm with the following three baseline algorithms (see figure \ref{baseline_algorithms}):
\begin{enumerate}
\item Vertical and horizontal linear interpolation,
\item Gaussian interpolation as described in section \ref{gaussian_interpolation} and
\item Matching pursuit~\cite{matchingpursuit93} with an overcomplete dictionary of discrete cosines.
\end{enumerate}

@@

Our algorithm did not perform equally well for all sample images: It worked best for ? (error ? and standard deviation ?) and worst for ? (error ? and standard deviation ?).

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Original image with mask (left) and its reconstruction (right).}
\label{edge_reconstruction}
\end{figure}
